Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 raspi_journal.tex
Ready for now..
Update Simon and Juan figures
Extracting the figures from the pdf does not look good
testbed and cross compilation
Setting goodput plots
Results structure done
Added abstract

@@

\usepackage[]{algorithm2e}

@@

% Authors, for the paper (add full first names)
\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3,4}$, Simon Wunderlich $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
% Authors, for metadata in PDF
\AuthorNames{Nestor Hernandez, Chres Soerensen, Juan Cabrera, Simon Wunderlich, Daniel Lucani and Frank Fitzek}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks. Dresden, Germany; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
$^{4}$ \quad SFB 912 -- Collaborative Research Center HAEC. Dresden, Germany}

@@

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{Due to the recurrent nature }

@@

@@

\section{Analyzed Metrics}
\input{metrics}

>>>>

\newcommand{\todot}[1]{%
  \textcolor{red}{TODO: #1}
}

@@

% *** ALGORITHM PACKAGE ***
\usepackage[]{algorithm2e}

% *** PDF PACKAGE *** ..to extract a page from a PDF with multiple pages.
\usepackage{pdfpages}

@@

% Authors, for the paper (add full first names)
\Author{N\'estor J. Hern\'andez Marcano $^{1,2,\dagger}$*, Chres W. S{\o}rensen $^{2,\dagger}$, Juan A. Cabrera G. $^{3,4}$, Simon Wunderlich $^{3}$, Daniel E. Lucani $^{2,\dagger}$ and Frank H. P. Fitzek $^{3}$}
% Authors, for metadata in PDF
\AuthorNames{Nestor Hernandez, Chres W. Soerensen, Juan Cabrera, Simon Wunderlich, Daniel E. Lucani and Frank H. P. Fitzek}  
% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Steinwurf ApS. Aalborg, Denmark; nestor@steinwurf.com\\
$^{2}$ \quad Aalborg University, Department of Electronic Systems. Aalborg, Denmark; \{nh, cws, del\}@es.aau.dk\\
$^{3}$ \quad Technische Universit\"at Dresden, Deutsche Telekom Chair of Communication Networks. Dresden, Germany; \{juan.cabrera, simon.wunderlich, frank.fitzek\}@tu-dresden.de\\
$^{4}$ \quad SFB 912 -- Collaborative Research Center HAEC. Dresden, Germany}

@@

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{Deploying a large-scale and configurable testbed for
  networking and storage can be challenging, not only due to the
  inherent costs of the hardware, but due to maintenance challenges
  and ability to replicate results consistently. The latter requires
  not only the devices to run the same operating system (OS), but also
  have exactly the same configurations and software packages. This
  paper presents the design, step-by-step setup, and configuration of
  an inexpensive testbed using Raspberry Pi devices for networking
  (wireless or wired) and storage applications, although the
  architecture can be used for other applciations that require
  replicable results.  Specifically, we provide an in-depth
  performance evaluation for network coding, a new paradigm in
  networking and storage, and demonstrating the processing
  capabilities and energy behaviour of various code constructions and
  algorithms over different Raspberry Pi models. Our results show that
  processing speeds of more than 80 Mbps and 800 Mbps are attainable
  for a wide array of configurations are attainable for the Raspberry
  Pi Model 1 and 2, respectively, and that processing energy for
  network coding is below 1 nJ/bit in a large regime and even an order
  of magnitude lower for some algorithms.}

@@

\section{Cross-compilation: From PC to Raspberry Pi}
\input{cross_compilation}

@@

\section{Metrics and Measurement Methodology}
\input{metrics}
